A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-12-03 paper/paper.tex
paper: polish Future Work

\begin{minted}{coq}
leR_trans ?p leR_refl = ?p
leR_trans leR_refl ?p = ?p
\end{minted}
%
where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \SProp, but equating them does not solve the existential. For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':

@@

\section{Future work}
The construction could be extended with degeneracies as well as with permutations~\citep{grandis03}. Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets. A $\nu$-set of $\nu$-sets representing a universe could also be defined (as sketched e.g. in a talk by Herbelin at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})). More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19}.

@@

Another direction for future work would also be to generically construct the indexed form of any presentation of presheaves over a direct category and to show the equivalence between the two presentations.

>>>>

\begin{minted}{coq}
leR_trans ?p leR_refl = ?p
leR_trans leR_refl ?p = ?p
\end{minted}

where \texttt{leR\_trans} is transitivity, \texttt{leR\_refl} is reflexivity, and \texttt{?p} is an existential variable. These two problems definitionally hold in \SProp, but equating them does not solve the existential. For unification to be useful in inferring existentials, we present our first variant of $\leq$, which we dub as the ``Yoneda variant'':

@@

\section{Future work}
The construction could be extended with degeneracies as well as with permutations~\citep{grandis03}. Dependent $\nu$-sets could also be defined, opening the way to construct $\Pi$-types and $\Sigma$-types of $\nu$-sets. A $\nu$-set of $\nu$-sets representing a universe could also be defined (as sketched e.g. in a talk at the HoTT-UF workshop for the bridge case~(\citeyear{herbelin-hott-uf})). More generally, we believe these lines of work to eventually provide alternative models to parametric type theories~\citep{nuyts17,cavallo19} where equality of types, now a family rather than the total space of a fibration, is not only definitionally isomorphic to bridges~\cite{bernardy15} but definitionally the same as bridges.

@@

Another direction for future work is to give a general definition of presheaf in indexed form over a direct category and to show the equivalence with the standard definition of presheaf.
